Panel Seminars

### 2023-02-13 index.Rmd
couple minor wording changes to index & contribution pages

# Making contributions to the MarineOmics website {#contributions}
We are excited to incorporate new material from contributors of various backgrounds, expertise, and experience. To date these tutorials, guidelines,  and discussions have been authored and led by graduate students and postdocs with contributions from scientists at all levels, including undergraduates, technicians, and faculty members. A diverse range of perspectives and backgrounds will make these tutorials more inclusive, informative, and useful for everyone in the marine-omics community. If you are interested in developing an information page or tutorial for the website,  we ask that you review our [page with instructions for submitting content](submissions_instructions.html) and contact our Website Manager Jason Johns (jasonjohns[at]ucsb.edu).

>>>>

# Making contributions to the MarineOmics.github.io website {#contributions}
We are excited to incorporate new material from contributors of various backgrounds, expertise, and experience. To date these tutorials, guidelines,  and discussions have been authored and led by graduate students and postdocs with contributions from scientists at all levels, including undergraduates, technicians, and faculty members. A diverse range of perspectives and backgrounds will make these tutorials more inclusive, informative, and useful for everyone in the marine-omics community. If you are interested in developing an information page or tutorial for the website,  we ask that you review our [page with instructions for submitting content](submissions_instructions.html) and contact our Website Manager Jason Johns (jasonjohns[at]ucsb.edu).
